---
title       : Course Project
subtitle    : Shiny Application and Reproducible Pitch
author      : Anthony Shuler
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This application is developed using R Programming  
language in R Studio's IDE. The application 
used shiny environment under R studio for interface 
desigening. 
This is a fairly good app can be used to provide iris
data dataset through datasets packages gives the 
measurements in centimeters of the variables sepal 
length and width and petal length and width, 
respectively, for 50 flowers from each of 3 species of 
iris. The species are Iris setosa, versicolor, and virginica.
The structure figure below illustration the variable for this 
application data:

```{r, echo=FALSE}
str(iris)

```

--- .
## Variables and Inputs
Using datasets package with the Iris to create this application illustration

Below are the lists of variables Iris provided:

- Sepal.Width
- Sepal.Length
- Petal.Width
- Petal.Length

Below is the type of input uses in application

- radio button 
- drop down
- tab panel
- reactive

--- .class #id 

## Interactive Charts

Where the input play the big role through the link provide below:

https://shuler1ad.shinyapps.io/reactive/

--- .

## Conclusion 
Where are able to show you the summary outcome of the application. 
```{r, echo=FALSE}
summary(iris)
```






